\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\section[From closed systems to continuous measurements]{From closed systems to continuous measurements --- in a nutshell}
In this chapter we will briefly summarize the definitions needed to our study.
\subsection[Quantum mechanics]{Generalities on quantum mechanics}
\subsubsection{States and time evolution}\label{Ii1}
In quantum mechanics a physical system's state is described by a vector in a Hilbert space:
\begin{equation}
    \ket{\psi}\in\mathcal{H}
\end{equation}

%  REECRIRE
The evolution of a system depends on its energy, the Hamiltonian $H$ is an hermitian\footnote{$\hat{H}^\dagger=\hat{H}$, where $^\dagger$ is the conjugate transpose operation, defining the hermitian adjoint. } operator that accounts for the total energy of a system. The Schrödinger equation states it explicitly: 
\begin{equation}
    i\hbar\frac{\mathrm{d}\ket{\psi(t)}}{\mathrm{d}t}=\hat{H}(t)\ket{\psi(t)}
\end{equation}

% MAL DIT
Instead of looking at the state at time $t$ we can use an unitary\footnote{$UU^\dagger=U^\dagger U=\mathbb{I}$, where $\mathbb{I}$ is the identity.} operator $\hat{U}$ such that, $\ket{\psi(t)}=\hat{U}(t,t_0)\ket{\psi(t_0)}$. From now on, we will omit the $\hat{}$ symbol over operators when it is obvious. We get, %Plus explicite, construire une phrase 
\begin{equation}
    \dot{U}(t,t_0)=-\frac{i}{\hbar}H(t)U(t,t_0)
\end{equation}

One can solve this differential equation in general by using a chronological time-ordering operator~\cite{Breuer}. Giving for the state evolution, % Mal écrit
\begin{equation}\label{Htimedep}
    \ket{\psi(t)} = \mathcal{T}_\leftarrow \exp\left[ -\frac{i}{\hbar}\int_{t_0}^t H(s) \mathrm{d}s\right]\ket{\psi(t_0)}
\end{equation}

Or, when the Hamiltonian is time-independent, %!!
\begin{equation}
    \ket{\psi(t)} = \underbrace{e^{-\frac{iH(t-t_0)}{\hbar}}}_{U(t,t_0)}\ket{\psi(t_0)}
\end{equation} 

% ecrire en 2 phrases (renverser l'ordre de causalité)
This evolution of the state with respect to time is said \textbf{unitary and reversible} because $U$ is unitary, and, because this equation also describes the time reversed evolution $t\rightarrow t_0$: $\ket{\psi(t_0)}=U^\dagger(t,t_0)\ket{\psi(t)}$~. %faux mathématiquement c'est pas la même équation
 
\subsubsection{Observables}
Any physical quantity is represented in quantum mechanics by an \textbf{observable}: an operator whose eigenvectors form an orthonormal basis of the Hilbert space $\mathcal{H}$~\cite{CT}. %refaire phrase suivante:
and whose eigenvalues are positive to represent a physical measurement. 
For finite dimension Hilbert space, hermitian operators\footnote{Hermitian operators always form a basis in finite dimension, and, we can use the Gram-Schmidt process to find its orthonormal version.Moreover, being a self-adjoint operator implies having real eigenvalues.} are observables. In the following, we will consider finite dimension and non-degenerate cases, b~\cite{CT}.\par %REECRIRE LA DERNIERE
A natural operator whose eigenbasis is particularly interesting is the Hamiltonian, whose eigenvalues correspond to the allowed energy values of a system. Let us denote $I_\mathcal{H}=\llbracket 1;\text{dim}(\mathcal{H})\rrbracket$ throughout this document.
\begin{equation}
    \forall n \in I_\mathcal{H},\quad H\ket{\phi_n} = E_n\ket{\phi_n} \label{EqPropreH}
\end{equation}
\par Let us call ${\left\{ \phi_n\right\}}_{n\in I_\mathcal{H}}$ the family of orthonormal eigenvectors of $H$ which forms a basis of $\mathcal{H}$.%bouger ça avant la formule
Since it forms a basis of the Hilbert space, one can describe any state in this very basis:
\begin{equation}
    \forall\ket{\psi}\in\mathcal{H},\qquad \ket{\psi} = \sum_{n\in I_\mathcal{H}} \underbrace{c_n}_{\braket{\phi_n}{\psi}}\ket{\phi_n}
\end{equation}
This kind of description in a base is obviously valid for any observable, not only for the Hamiltonian. We can complete this part with the normalization of the state, for proper handling of scalar products, we need to set $\left|\psi\right|=\sqrt{\braket{\psi}{\psi}}=1$. The condition $\braket{\psi}{\psi}=\sum_n |c_n|^2=1$ is thus equivalent.

\subsubsection{Purity of states}
Taking the qubit example, let $\alpha,\beta\in\mathbb{C}$ to write the qubit state as a superposition of excited/ground state as:
\begin{equation}\label{superposition}
    \ket{\psi} = \alpha\ket{e}+\beta\ket{g}\qquad\text{where, }\abs{\alpha}^2+\abs{\beta}^2=1 
\end{equation}
By getting ahead of QMT, we can introduce the probability to find a system in one of the possible eigenstates of an observable. Let us take the following example, what is the probability to find the energy $E_n$, defined by Eq.\ (\ref{EqPropreH}), from a system in $\ket{e}$ state? From a system in $\ket{g}$ state?
\begin{align}
    \mathbb{P}_e [E_n]&=\abs{\braket{\phi_n}{e}}^2\\
    \mathbb{P}_g [E_n]&=\abs{\braket{\phi_n}{g}}^2
\end{align}
A physical state can be, by the concepts of quantum mechanics, a mixture of statistical probabilities~\cite{CT}. Let us now consider back the superposition from Eq.\ (\ref{superposition}), a physical mixture would be described by mixing states $\ket{e},\ket{g}$ with weights $\abs{\alpha}^2,\abs{\beta}^2$:
\begin{equation}
    \mathbb{P}_\psi [E_n]\overset{?}{=}\abs{\alpha}^2~\mathbb{P}_e [E_n]+\abs{\beta}^2~\mathbb{P}_g [E_n]
\end{equation}
In fact, quantum mechanics gives the exact value of this probability:
\begin{align}
    \mathbb{P}_\psi [E_n]&=\abs{\braket{\phi_n}{\psi}}^2\\
    &= \abs{\alpha}^2\abs{\braket{\phi_n}{e}}^2+\abs{\beta}^2\abs{\braket{\phi_n}{g}}^2+2\Real\left\{\alpha\beta^*\braket{\phi_n}{e}\braket{\phi_n}{g}^*\right\}
\end{align}
The statistical mixture terms appear but also cross terms in the true probability of finding the superposition in one of the eigenstates. This notion of hidden correlations due to superposition has been highlighted by a new formalism, \textbf{density matrices}.\par
Basically, instead of a ket $\ket{\psi}$ we describe a system by a density matrix $\rho$ which, for \textbf{pure} systems is simply: 
\begin{equation}
    \rho_\text{p} = \ketbra{\psi}{\psi}
\end{equation}
The density matrix is thus an operator of Hilbert space elements\footnote{$\rho$ is also an operator of the dual, $\mathcal{H}^*$ because we find that $\bra{\phi_j}\rho\propto\bra{\phi_j}$.\\We could even ague that $\rho\in\mathcal{L(H)}$\ldots} $\rho:\mathcal{H}\rightarrow\mathcal{H}$. For a \textbf{statistical mixture}, thus non-pure, the density matrix in a basis $\qty{\phi_n}_{n\in I_\mathcal{H}}$ takes the form:
\begin{equation}
    \rho_\text{sm} = \sum_{n\in I_\mathcal{H}} \mathbb{P}_n \ketbra{\phi_n}{\phi_n} 
\end{equation}
The components of the matrix are precisely, on the diagonal, the probabilities to find the state of the system in one of the eigenstates of the observable. The off-diagonal components are called \textbf{coherences}, they represent interference effects between the eigenstates, they can appear when the system's state is a linear coherent superposition of these eigenstates~\cite{CT}.\par
The mathematical definition of a density matrix is in any case~\cite{CT,Breuer}:
\begin{itemize}
    \item $\rho$ is hermitian $\rho^\dagger=\rho$
    \item $\rho$ is semi-definite $\forall\ket{\alpha}\in\mathcal{H},\quad\bra{\alpha}\rho\ket{\alpha}\geq  0$
    \item $\rho$ respects $\Tr{\rho}=1$
\end{itemize}

\subsubsection{Postulates of quantum mechanics}
Physicists developed a corpus of the main properties of quantum mechanics, here are summarized the so-called postulates of quantum mechanics~\cite{CT}:
\begin{enumerate}
    \item The state of a system is represented by a density matrix $\rho\in\mathcal{L(H)}$. For pure states we can describe them using the Dirac formalism $\ket{\psi}\in\mathcal{H}$, or using the pure matrix density formalism $\rho_p=\ketbra{\psi}{\psi}$. 
    \item Physical quantities $\mathcal{A}$ are associated with operators $\hat{A}$, called observables. In the context of finite dimension space, they are simply Hermitian operators.
    \item The only possible outcomes of a measurement of $\mathcal{A}$ are the eigenvalues $a$ of $\hat{A}$, defined by $\hat{A}\ket{a}=a\ket{a}$~.
    \item When measuring $\mathcal{A}$ on a normalized state, we know the probability to get one of the possible eigenvalues: $\mathbb{P}(a_n)$ (which depends on the spectrum of the observable).
    \item If the measurement of the physical quantity $\mathcal{A}$ on the system gives the result $a_n$, the state of the system immediately after the measurement collapses into the eigenstate $\ket{\phi_n}$.
    \item The time evolution of the wavefunction $\ket{\psi(t)}$ is governed by the \textit{Schrödinger} equation:
    \begin{equation*}
    \frac{\mathrm{d}\ket{\psi(t)}}{\mathrm{d} t}=-\frac{i}{\hbar}H(t)\ket{\psi(t)}
    \end{equation*}
    For density matrices, the evolution is driven by the \textit{Liouville-von Neumann} equation\footnote{$[\hat{A},\hat{B}]=\hat{A}\hat{B}-\hat{B}\hat{A}$ is the commutator of $\hat{A}$ and $\hat{B}$}:
    \begin{equation}
        \frac{\mathrm{d}\rho}{\mathrm{d}t}(t) = -\frac{i}{\hbar}\left[ H(t),\rho(t)\right]\equiv\mathcal{L}(t)\rho(t)
    \end{equation}
    
\end{enumerate}
\subsection[Open quantum systems]{Open Quantum Systems (OQS)}\label{OQS}
\setlength{\parskip}{2mm}
In the previous part, we saw that one can fully describe a system, observables, states and their evolution. We recall that this description is ideal in the sense that the system is considered to be completely isolated from any interaction with its environment. %The previous description applies to the ideal case, ...
In this section, we introduce the concepts of OQS which lead to a more physical description of quantum mechanics.\par
It is important to understand that the total system is a closed system, the total system space is mathematically $\mathcal{H} % on tronque localement pour définir E 
_T=\mathcal{H}_S\otimes\mathcal{H}_E$~. The total system $T$ thus follows a unitary time evolution, but, it is not the case for the physical system of interest $S$. Another of dynamics will arise for $S$ due to its coupling with $E$.
this is why we call $S$ an open quantum system.\par %mal dit

By following the formalism of reference~\cite{Breuer}, we need to jump in a different representation of the equations: the interaction picture. %Pour ??
In the \textit{Schrödinger} picture, states evolve with respect to time, observables can be constants or depend explicitly on time. Instead, in the \textit{Heisenberg} picture it is the opposite, observables carry the whole dynamics and states are constants (see Eq.~\ref{eq:HSlink}). The interaction picture is a mix of both, where states and observables are functions of time.\par

Interaction picture begins with the perturbation theory, where we split the Hamiltonian in two parts, the free Hamiltonian $H_0$ and the interaction Hamiltonian $H_I$ %Réécrire
\begin{align}
    H_T &= \overbrace{H_S\otimes\mathbb{I}_E+\mathbb{I}_S\otimes H_E}^{H_0}+H_I\label{eq:Htotal}\\
    U(t,t_0) &= U_0(t,t_0)U_I(t,t_0)\label{eq:Utotal}
\end{align}
We define the interaction Hamiltonian by,
\begin{align}
    E_n(t) &= U^\dagger_0(t)E_n U_0(t)\\
    H_I(t) &= \sum_{n\in I_\mathcal{H}}\overbrace{\ketbra{n}{n}}^{A_n}\otimes E_n(t)
\end{align}
We can then find the useful following relations:
\begin{align}
    \tilde{\rho}(t)&=U_I(t)\rho_{S}U_I^\dagger(t)= U^\dagger_0(t)\rho_S(t)U_0(t)\label{eq:rhoIP}\\
    \tilde{O}(t) &= U_0^\dagger(t)O_S(t)U_0(t)\label{eq:OIP}
\end{align}

One can then find the equation that governs the dynamics of $\rho_S$\footnote{Here and in the following, $\rho_S$ is the state of the system obtained by tracing out the environnement from the total state: $\rho_S=\mathrm{Tr}_E\, [\rho]$} in the \textit{Schrödinger picture} by making progress in the \textit{interaction picture}. We call this equation the \textit{Redfield Master Equation} but its expression is analytically formal. To go further, one needs to make important assumptions known as the \textit{Born-Markov} approximations and the \textit{secular} approximation.\par
\newpage
$\blacklozenge\quad$The \textit{Born} approximation consists in saying that the environment acts as a thermodynamical reservoir, \textit{i.e.}, the environment is so big compared to the system that the interaction does not alter its state:
\begin{equation}
    \tilde{\rho}_T(t) = \tilde{\rho}_S(t)\otimes\rho_E
\end{equation}
It describes a so-called ``weak-coupling'' between the system and the environment.\par

$\blacklozenge\quad$The \textit{Markov} approximation assures that the entire system has no memory. That is to say, the environment is so rapidly agitating that it dissipates information of the system instantaneously. This implies that the environment comes back to equilibrium instantaneously after each interaction. Physically, the timescale of the reservoir correlation function decay $\tau_E$ is smaller than the timescale $\tau_R$ on which the system varies ``appreciably''.\par %inexact
These two last approximations lead to the \textit{Markovian quantum master equation}.\par
$\blacklozenge\quad$The \textit{secular} approximation allows the possibility to neglect rapidly oscillating terms in the quantum \textit{Markov} master equation.

\subsection[Quantum measurement theory]{Quantum Measurement Theory (QMT)}

