% ACKNOWLEDGEMENTS PAGE
\newpage\thispagestyle{empty}
\centering {\Huge \textbf{ACKNOWLEDGEMENTS}}
\vskip 2.5mm
\noindent\rule{\textwidth}{0.8pt}\\[-3    mm]
\noindent\rule{\textwidth}{0.8pt}
\vskip 5mm
\begin{justify}
    \hspace{0.5cm}The author expresses deep gratitude to Bruno Bellomo for his guidance and support throughout this research. Bruno, as a mentor, constantly took the time to explore ideas, ensure our understanding, and seek details. His expertise in Quantum Mechanics has been fundamental to the successful completion of this Master’s thesis. I am grateful to conclude my short career as a physicist with such a demanding journey, thanks to Bruno.\par\vspace{0.15cm}\noindent
    I would like to thank the members of the jury for their time and interest in this work, as well as for the opportunity to present my work in front of such esteemed peers.\par\vspace{0.15cm}\noindent
    I also would like to thank my colleagues, of a few months, for their insightful discussions and support during this internship: Silvio Da Silva, Jana El Badawi, Anjana Mohan, and Léo Jacquerot-Legros.\par\vspace{0.15cm}\noindent
    Finally, I would like to thank my friends and family for their never-ending support: Erwan Le D{\oe}uff, Titouan Alphonse, and Nabyan Arkan for these two years of Master’s studies and friendship together, also, thank to Maxence Bonin and Vincent Girod my brothers from other mothers. I owe everything to my parents, Catherine and Lionel, for my life and education, and, to my brother Pierre who is so resilient and skillful. Lastly, I want to thank my other half, Alexiane.
\end{justify}
\rule{0.5\textwidth}{1pt}\par
\vspace{0.25cm}
\begin{justify}
    \hspace{0.5cm}L'auteur exprime sa profond gratitude envers Bruno Bellomo pour ses conseils et son soutien tout au long de ce travail de recherche. Bruno, en tant que mentor, a constamment pris le temps d'explorer des idées, de s'assurer de notre compréhension et d'approfondir les détails. Son expertise en mécanique quantique a été fondamentale dans la bonne conduite de ce mémoire de master. Je suis reconnaissant de pouvoir conclure ma courte carrière de physicien par un parcours aussi exigeant, grâce à Bruno.\par\vspace{0.15cm}\noindent
    Je tiens à remercier les membres du jury pour le temps et l'intérêt qu'ils porteront à ce travail, ainsi que pour l'opportunité de le présenter devant des pairs reconnus.\par\vspace{0.15cm}\noindent
    Je souhaite tout de même remercier mes collègues de quelques mois pour leurs discussions enrichissantes et leur soutien durant ce stage: Silvio Da Silva, Jana El Badawi, Anjana Mohan et Léo Jacquerot-Legros.\par\vspace{0.15cm}\noindent
    Enfin, je tiens à remercier mes amis et ma famille pour leur soutien indéfectible~: Erwan Le D{\oe}uff, Titouan Alphonse et Nabyan Arkan pour ces deux années d'études de Master et amitié partagées, mais également, merci à Maxence Bonin et Vincent Girod mes frères d'autre mères. Je dois tout à mes parents, Catherine et Lionel, pour ma vie et mes études, ainsi qu'à mon frère Pierre qui sait être résilient et plein de ressources. Pour finir, je remercie ma meilleure moitié et compagne, Alexiane.
\end{justify}
\vfill
\begin{flushright}
    \small{\textit{« La gloire de Dieu, c'est de cacher les choses; La gloire des rois, c'est de sonder les choses. »} \\
    \textbf{— Proverbes 25:2}}
\end{flushright}\newpage

\justifying
\normalsize % SIZE OF CONTENTS!!!
\tableofcontents
\addtocontents{toc}{\protect\thispagestyle{empty}}