\subsection[Open quantum systems]{Open Quantum Systems (OQS)}\label{OQS}
\setlength{\parskip}{2mm}
In the previous part, we saw that one can fully describe a system, observables, states and their evolution. We recall that this description is ideal in the sense that the system is considered to be completely isolated from any interaction with its environment. %The previous description applies to the ideal case, ...
In this section, we introduce the concepts of OQS which lead to a more physical description of quantum mechanics.\par
It is important to understand that the total system is a closed system, the total system space is mathematically $\mathcal{H} % on tronque localement pour définir E 
_T=\mathcal{H}_S\otimes\mathcal{H}_E$~. The total system $T$ thus follows a unitary time evolution, but, it is not the case for the physical system of interest $S$. Another of dynamics will arise for $S$ due to its coupling with $E$.
this is why we call $S$ an open quantum system.\par %mal dit

By following the formalism of reference~\cite{Breuer}, we need to jump in a different representation of the equations: the interaction picture. %Pour ??
In the \textit{Schrödinger} picture, states evolve with respect to time, observables can be constants or depend explicitly on time. Instead, in the \textit{Heisenberg} picture it is the opposite, observables carry the whole dynamics and states are constants (see Eq.~\ref{eq:HSlink}). The interaction picture is a mix of both, where states and observables are functions of time.\par

Interaction picture begins with the perturbation theory, where we split the Hamiltonian in two parts, the free Hamiltonian $H_0$ and the interaction Hamiltonian $H_I$ %Réécrire
\begin{align}
    H_T &= \overbrace{H_S\otimes\mathbb{I}_E+\mathbb{I}_S\otimes H_E}^{H_0}+H_I\label{eq:Htotal}\\
    U(t,t_0) &= U_0(t,t_0)U_I(t,t_0)\label{eq:Utotal}
\end{align}
We define the interaction Hamiltonian by,
\begin{align}
    E_n(t) &= U^\dagger_0(t)E_n U_0(t)\\
    H_I(t) &= \sum_{n\in I_\mathcal{H}}\overbrace{\ketbra{n}{n}}^{A_n}\otimes E_n(t)
\end{align}
We can then find the useful following relations:
\begin{align}
    \tilde{\rho}(t)&=U_I(t)\rho_{S}U_I^\dagger(t)= U^\dagger_0(t)\rho_S(t)U_0(t)\label{eq:rhoIP}\\
    \tilde{O}(t) &= U_0^\dagger(t)O_S(t)U_0(t)\label{eq:OIP}
\end{align}

One can then find the equation that governs the dynamics of $\rho_S$\footnote{Here and in the following, $\rho_S$ is the state of the system obtained by tracing out the environnement from the total state: $\rho_S=\mathrm{Tr}_E\, [\rho]$} in the \textit{Schrödinger picture} by making progress in the \textit{interaction picture}. We call this equation the \textit{Redfield Master Equation} but its expression is analytically formal. To go further, one needs to make important assumptions known as the \textit{Born-Markov} approximations and the \textit{secular} approximation.\par
\newpage
$\blacklozenge\quad$The \textit{Born} approximation consists in saying that the environment acts as a thermodynamical reservoir, \textit{i.e.}, the environment is so big compared to the system that the interaction does not alter its state:
\begin{equation}
    \tilde{\rho}_T(t) = \tilde{\rho}_S(t)\otimes\rho_E
\end{equation}
It describes a so-called ``weak-coupling'' between the system and the environment.\par

$\blacklozenge\quad$The \textit{Markov} approximation assures that the entire system has no memory. That is to say, the environment is so rapidly agitating that it dissipates information of the system instantaneously. This implies that the environment comes back to equilibrium instantaneously after each interaction. Physically, the timescale of the reservoir correlation function decay $\tau_E$ is smaller than the timescale $\tau_R$ on which the system varies ``appreciably''.\par %inexact
These two last approximations lead to the \textit{Markovian quantum master equation}.\par
$\blacklozenge\quad$The \textit{secular} approximation allows the possibility to neglect rapidly oscillating terms in the quantum \textit{Markov} master equation.